Computer Science House Constitution

### 2022-02-14 constitution.tex
Add Active Member Requirement for Elections

\asubsection{Waiving of Requirements}
\begin{enumerate}
  \item The following requirements may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must have at least one full semester of House membership as an Active Member
      \item Candidates must reside on floor during the term of office
    \end{enumerate}
  \item This process waives the enumerated requirements for a given election for all candidates on a per-directorship basis
\end{enumerate}

@@

>>>>

@@

	\item The date and time of the candidate(s)'s speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. This will be treated as a House Meeting, with the expectation that all Active Members will attend and attendance will be taken. If the speeches take place at a traditional House Meeting, only one attendance will be taken.
